\documentclass[a4,12pt]{article}
\usepackage{fontawesome5, fontspec, url, parskip, hyperref, color, graphicx, tabularx, enumitem, titlesec, xcolor, geometry}
\geometry{scale=0.9}
\definecolor{linkcolour}{rgb}{0,0.2,0.9}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\newcolumntype{C}{>{\arraybackslash}X}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{8pt}
\pagestyle{empty}
\begin{document}

% Header Section
\begin{tabularx}{\linewidth}{@{}C@{}}
\Huge{Nathan Paul} \\[10pt]
\href{https://polarhive.net}{\faIcon{globe} polarhive.net/contact} \ $|$ \
\href{https://github.com/polarhive}{\faIcon{github} polarhive} \ $|$ \
\href{https://linkedin.com/in/polarhive}{\faIcon{linkedin} polarhive} \ $|$ \
\href{https://polarhive.net/email}{\faIcon{envelope} 0x78DBFBE8B325A5A9}
\end{tabularx}

% Experience Section
\section{Experience}

\textbf{Research Intern} @ \textbf{\href{https://theinnovationlab.in}{PES Innovation Lab}} (formerly Microsoft Innovation Lab) \hfill June '25 – Jul '25 \\
• Project Intern, team \textbf{MiCozServices} \\
• Investigated tuning techniques to profile Microservices \\
• Work based on the Causal Profiling paper: \textbf{\href{https://dl.acm.org/doi/10.1145/2815400.2815409}{Coz}}

\textbf{Platform Engineering Intern} @ \textbf{\href{https://golain.io}{Golain.io}}. Remote, Pune \hfill Mar '25 – Apr '25 \\
• Migration toward a \textbf{DAG}-based workflow engine to improve system scalability \\
• Assisted in refactoring components of the codebase to simplify rule-logic and modularity

\textbf{Developer}, \textbf{ACM Industrial Experience Program} \hfill Feb '24 – Apr '24 \\
• Part of the team that built \textbf{anna}, a static site generator written in Go. \\
• Achieved \textbf{284.5 ms} render time for a 1000-file \href{https://github.com/anna-ssg/anna/actions}{benchmark}, outperforming Hugo and 11ty. \\
• Created a sitemap generator, set up RSS feeds, and an interactive tag-graph (D3.js). \\
• \textbf{DevOps:} Implemented CI/CD pipelines, a setup wizard, and theme bootstrapping. \\
• Presented at the \href{https://www.meetup.com/golang-bangalore/events/301697429/}{76th Go Bangalore meetup}.

% Skills Section
\section{Skills}
\textbf{Languages:} Go, Python, Bash, C, Nix, CSS, Redis, Postgres \\
\textbf{Technologies:} Git, Docker, GNU/Linux, Vim, Observability \\
\textbf{Writing, Communication:} Blogging, \LaTeX, Free Software Documentation, RFCs

% Interests Section
\section{Interests}
Free Software
• Privacy
• Protocols
• GNU/Linux
• Systems
• IoT
• Startups
• Zero Knowledge Proofs

% Projects Section
\section{Projects}
• \textbf{\href{https://github.com/anna-ssg/anna}{anna}}: Lightning-fast static site generator written in Go. \\
• \textbf{\href{https://github.com/polarhive/py-typer}{py-typer}}: A speed typing test written in Python. \\
• \textbf{\href{https://polarhive.net/pasta}{pasta}}: Minimal pastebin service written in Go. \\
• \textbf{\href{https://github.com/polarhive/jukebox}{jukebox}}: Queue LastFM music recommendations using \textbf{mpd}, \textbf{yt-dlp}, and Python. \\
• \textbf{\href{https://polarhive.net/lava}{lava}}: Node daemon that periodically saves bookmarked articles to your Obsidian vault. \\
• \textbf{\href{https://github.com/polarhive/wombat}{wombat}}: Wikipedia crawler that visualizes relationships between articles. \\
• \textbf{\href{https://polarhive.net/bullet}{bullet}}: Collates similar articles from various RSS feeds using cosine similarity. \\
• \textbf{\href{https://github.com/polarhive/drago}{drago}}: DAG-based workflow engine (PoC)


% Misc Section
\section{Links}
• \textbf{\href{https://polarhive.net/pow}{Proof of Work}}: A reverse chronological record of my work. \\
• \href{https://polarhive.net/videos}{Videos}: YouTube channel focused on tech, privacy, and libre software.\\
• \href{https://polarhive.net/photos}{Photos}: Photos that I have shot and edited. \\
• \href{https://polarhive.net/ammachiskathas}{Ammachis Kathas}: Malayalam short stories (an audiobook). \\
• \href{https://polarhive.net/arceo}{arceo}: Blocklist against social media, news \& consumerism. \\
• \href{https://polarhive.net/wiki}{wiki}: My digital garden, a linkstash with web clippings.

% Education Section
\section{Education}
\textbf{B.Tech in Computer Science \& Engineering} at PES University \hfill 2023 – 2027 \\
\textbf{ISFCR Dean's Award:} Ranked 6th out of 250 participants in a jeopardy-style CTF.

\textbf{Mentor Lead @HSP PESU} \hfill June '25 – Present \\
• Leading the mentor team and coordinating club-wide initiatives \\
• In charge of \textbf{Tilde 4.0}, HSP's flagship summer-mentorship program \\
• Overseeing technical contributions and workshops for the '26 term

\textbf{Technical Mentor @HSP PESU} \hfill Oct '23 – May '25 \\
• Maintainer of the club \href{https://tiramisu-hsp.netlify.app}{website}, powered by anna \\
• Mentored contributors to \href{https://github.com/homebrew-ec-foss/psh}{psh}, a POSIX-like shell \\
• Presented \textbf{jukebox} and \textbf{anna} at HSP Mentor Expo and Fireside Talks

\textbf{Member @ACM PESU} \hfill Sept '23 – Present \\
• Maintainer Lead for Hacknight 6.0 \\
• Mentored contributors to \href{https://github.com/polarhive/nimbus}{nimbus}, a TUI client for Bluesky

\textbf{Member @GDSC PESU} \hfill Aug '23 – Sept '24 \\
• Hosted \href{https://polarhive.net/talks/gdsc-foss-101/}{FOSS 101}, an introductory workshop on open source \\
• Designer for Override, a Google Solutions Challenge hackathon

\noindent\rule{\textwidth}{0.4pt}

\href{https://github.com/polarhive/resume}{\faIcon{history}} \today

\end{document}
